%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks=true,urlcolor=black]{hyperref} % Hyperlink

\name{Wei Cui} % Your name
\address{Room 3514, Beckman Institute \\ University of Illinois} % Your addess
\address{405 N. Mathews Ave. \\ Urbana, IL 61801} % Your secondary addess (optional)
\address{Tel: (217)305-1663 \\ E-mail: wc2@illinois.edu} % Your phone number and email

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Education}
		
		{\bf Ph.D. Student in Electrical Engineering} \hfill {\em Aug. 2016 -- Now} \\ 
		University of Illinois at Urbana-Champaign\\
		Project: \textit{Near-eye 3D Displays}\\
		Research Assistant at Intelligent Optics Lab\\
		
		{\bf M. Eng. in Optical Engineering} \hfill {\em Sept. 2013 -- Apr. 2016} \\ 
		Zhejiang University \\
		Thesis: \textit{High-resolution Multi-channel FBG Temperature Sensing System}\\
		Comprehensive Ranking: \textbf{Top 10\%} \\
		
		{\bf B. Eng. in Optoelectronic Engineering} \hfill {\em Sept. 2009 -- Jun. 2013} \\ 
		Chongqing University \\
		Academic Ranking: \textbf{2/83}\\
		Cumulative GPA: \textbf{3.55/4}\\
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Experience}
		
		\begin{rSubsection}{Near-eye 3D Display with Correct Focus Cues}{Aug. 2016 -- Apr. 2017}{Intelligent Optics Lab, Department of Electrical and Computer Engineering}{University of Illinois}
			\item Proposed an \textbf{optical mapping method} for near-eye 3D displays (OMNI)
			\item Implemented and verified a \textbf{prototype} of OMNI displays
			\item Designed and optimized the adaptive \textbf{phase pattern} for OMNI displays
		\end{rSubsection}
		
		\begin{rSubsection}{High-resolution Multi-channel FBG Temperature Sensing System}{Apr. 2014 -- Sept. 2015}{Photonics Technology Lab, College of Optical Science and Engineering}{Zhejiang University}
			\item Focused on \textbf{system setup} and \textbf{demodulation algorithm} for FBG sensing network
			\item Applied FPGA \& PDs to guarantee \textbf{quasi-distributed} sensing \& \textbf{real-time} demodulation
			\item Obtained \textbf{1pm resolution and accuracy} by LD modulation and F-P reference
		\end{rSubsection}
		
		\begin{rSubsection}{"National Instrument Cup" Virtual Instrument Design Competition}{Dec. 2013 -- Apr. 2014}{College of Biomedical Engineering \& Instrument Science}{Zhejiang University}
			\item \textbf{Proposed the idea} of music performance evaluation by chronological tone matching
			\item Utilized \textbf{DAQ card} and \textbf{LabVIEW} to program and solve data acquisition and analysis
			\item Applied \textbf{DFT} for spectral estimation and \textbf{Butterworth} filter for higher \textbf{SNR}
		\end{rSubsection}
		
		\begin{rSubsection}{Design of Magnetic Field Sensor based on Micro-nano Fiber}{Sept. 2012 -- June. 2013}{Fiber \& Photonics Lab, College of Optoelectronic Engineering}{Chongqing University}
			\item Focused on \textbf{micro-nano fiber making} through heating and tapering
			\item Employed \textbf{magneto fluid coating} for weak magnetic field sensing
			\item Designed a three-section-taper \textbf{structure for the sensor}
		\end{rSubsection}
		
		\begin{rSubsection}{Mathematical Modeling}{Apr. 2011 -- Apr. 2012}{College of Mathematics and Statistics}{Chongqing University}
			\item Described practical issues using \textbf{precise mathematical language} and models
			\item Utilized MATLAB to \textbf{program and solve} mathematical models
			\item Tested these models and results by \textbf{robust analysis}, sensitivity analysis and error analysis
		\end{rSubsection}
		
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	AWARDS SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Awards}
		\begin{rSubsection}{Honorable Mention in Mathematical Contest in Modeling (MCM)}{Feb. 2012}{}{}
			\item Awarded by the Consortium for Mathematics and its Application (COMAP), U.S.
		\end{rSubsection}
		
		\begin{rSubsection}{First Prize of China Undergraduate Mathematical Contest in Modeling}{Sept. 2011}{}{}
			\item Awarded by Chinese Society for Industrial and Applied Mathematics, Chongqing Arena
		\end{rSubsection}
		
		\begin{rSubsection}{Foxconn Enterprise Scholarship}{Dec. 2010}{}{}
			\item Funded students with both outstanding academic and project research performance (\$300)
		\end{rSubsection}
		
		\begin{rSubsection}{Chongqing University Comprehensive Scholarship}{2010 -- 2012}{}{}
			\item Obtained the scholarship \textbf{all 6 times} for three consecutive years ($\$150\times6$)
			\item Awarded \textbf{top 10} students in College of Optoelectronic Engineering
		\end{rSubsection}
		
		\begin{rSubsection}{Advanced Individual for Scientific and Technological Innovation}{Dec. 2010}{}{}
			\item Awarded \textbf{top 20} students of Chongqing University by Chongqing Government
		\end{rSubsection}
		
		\begin{rSubsection}{Excellent Student Community Leader}{Dec. 2011}{}{}
			\item Awarded \textbf{top 20} student leaders of Chongqing University
		\end{rSubsection}
		
	\end{rSection}
	
	% ----------------------------------------------------------------------------------------
	% 	LANGUAGE SECTION
	% ----------------------------------------------------------------------------------------
	
	\begin{rSection}{Language}
		
		\begin{tabular}{ l l r}
			BEC (Higher) & \textbf{Pass} at Grade C & May. 2015 \\
			TOEFL(iBT) & Total \textbf{100}: Reading 27, Listening 24, Speaking 22, Writing 27 & Aug. 2014 \\
			GRE(General) & Total \textbf{318}: VR 150, QR 168, AW 3.5 & Mar. 2012 \\
		\end{tabular}
		
	\end{rSection}
	
	% ----------------------------------------------------------------------------------------
	% 	SKILLS SECTION
	% ----------------------------------------------------------------------------------------
	
	\begin{rSection}{Skills}
		
		Mastery of \textbf{LabVIEW} DAQ Module \\
		Proficiency in optical design using \textbf{ZEMAX} \\
		Familiar with precise mechanical design using \textbf{SolidWorks} \\
		Intermediate level of \textbf{C}, \textbf{VHDL} and \textbf{Verilog} programming language
		
	\end{rSection}
	
	% ----------------------------------------------------------------------------------------
	% 	PUBLICATION SECTION
	% ----------------------------------------------------------------------------------------
	
	\begin{rSection}{Publications}
		
		\href{http://www.photon.ac.cn/CN/article/downloadArticleFile.do?attachType=PDF&id=21225}{\textbf{Wei Cui}, Jianjia Su, Peipei Jiang, et al. \textit{High-Resolution Multiplexed Fiber Bragg Grating Wavelength Interrogation System Based on Tunable LD}, ACTA PHOTONICA SINICA, 45(7):0706003, 2016.}
		
		\href{http://www.sciencedirect.com/science/article/pii/S0263224116303360}{Jianjia Su, Peipei Jiang, \textbf{Wei Cui}, et al. \textit{Novel digital iteration algorithm for fluorescence lifetime measurement of multi-probe fiber thermometer}, MEASUREMENT, 92 (2016): 428-432.}
		
		\href{http://www.photon.ac.cn/article/2016/1004-4213-45-7-706001.html#close}{Jianjia Su, Peipei Jiang, \textbf{Wei Cui}, et al. \textit{Multi-probe Fiber Thermometer Based on Sapphire-ruby Fiber Sensing Head}, ACTA PHOTONICA SINICA, 45(7):0706001, 2016.}
		
		\href{http://iopscience.iop.org/article/10.1088/1612-2011/11/12/125103/meta}{Dacheng Hua, Jianjia Su, \textbf{Wei Cui}, et al. \textit{All-fiberized SBS-based high repetition rate sub-nanosecond Yb fiber laser for supercontinuum generation}, LASER PHYSICS LETTERS, 11(12), Dec. 2014.}
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	
\end{document}
